---
title: "Social Survey 2010"
author: "Geyli Stephanie Contreras"
date: "Fall 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyvertse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Use the data from the 2010 general social survey to explore whether belief in continental drift (condrift), views on capitol punishment (cappun), and race (race) are independent of each other.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
In order to see if the different beliefs are independent of each other we will be analysing the data by separating the people in the survey by race and comparing the results using bar graphs. Different variables are to be considered such as race miratal status, race, age etc. There are 790 variables to be considered when making the graphs.   
  

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
alldata <- read.csv(file="gss2010.csv", header=TRUE)
names(alldata)
```


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
barchartGC(~race+condrift, data=alldata, type = "percent") 
```  
  
From the graph we can see that there is no much difference between white and other when it comes to the opinion about the continental drift. The amount of "white" and "other" that belief that it is true or false is almost the same. There is little or no difference at all between "other" and "white" opinion. But there's a difference between "black" and the other two results. Black's FALSE results is almost the triple than the other two. And the true results are lower.   
  
```{r}
barchartGC(~race+cappun, data=alldata, type = "percent")   
```
    
The graph shows that blacks oppose capital punishtment and white favor it. More than half of the white people favor capital punishment; in the other hand more blacks oppose it. There is a little bit of similarity between white and other. More of the "other" favor it, and and while they oppose it more than whites they still favor it.      
  
  

```{r}
barchartGC(~condrift+cappun, data=alldata, type = "percent")    
```
  
In result, this graph shows that the people who beliefe continental drift is false they favor the capital punishment. Also the peole who says that the continental drift is true thet also favor the capital punishment. We can clearly see here that the opinons are about the same.   


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
tab = xtabs(~race+condrift, data=alldata)
rowPerc(tab)
colPerc(tab)
```
  
```{r}
tab = xtabs(~race+cappun, data=alldata)
rowPerc(tab)
colPerc(tab)
```


```{r}
tab = xtabs(~cappun+condrift, data=alldata)
rowPerc(tab)
colPerc(tab)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~race+condrift, data=alldata, graph=TRUE)
```

```{r}
chisqtestGC(~race+cappun, data=alldata, graph=TRUE)
```
  
```{r}
chisqtestGC(~cappun+condrift, data=alldata, graph=TRUE)
```

After observing the 3 grapsh we rejected the null hypothesis because the p value was very low. In the three diffent graphs we see how the null hypothesis is no where close to the real numbers.   
  



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->  
I believe there a  relationship between them because the results are almost the same when it comes to "white" and "others". "black" results where a little different about the capital punishment but overall all of the 3 races voted fairly similar. 